---
output: github_document
---
# Final Project-Group 1

[Package Repository: FinalProject](https://github.com/AU-R-Programming/FinalProject)

The package is called "lmG1" under the "AU-R-Programming/FinalProject" repository. 
The package is designed to perform linear regression where the parameter vector
beta is estimated using optimization. The package can be download by using
"devtools::install_github("AU-R-Programming/FinalProject")"function. Learn more about 
the lmG1 function in the vignette below.

To start off, there are two variables that need to be initialized by the user: 

    `x`: predictor variables, which is represented by a matrix of dimension n × p.
    
    `y`: response variable of interest, a vector that we want to predict.

We are using the `crop.data.csv` as our example data set. 

```{r linear_regression_preprocess, warning = FALSE, message = FALSE}
library(devtools)
devtools::install_github("AU-R-Programming/FinalProject")

library(lmG1)
crop_data <- read.csv("crop.data.csv", header = TRUE)

set.seed(1)
crop_data <- na.omit(crop_data)
density <- as.factor(crop_data$density)
block <- as.factor(crop_data$block)
fertilizer <- as.factor(crop_data$fertilizer)
X <- cbind(density, block, fertilizer)
y <- crop_data$yield
```

```{r linear_regression_plots, warning = FALSE, message = FALSE}
result <- lmG1(y, X, alpha = 0.05, plot = TRUE)
```

```{r linear_regression_results, warning = FALSE, message = FALSE}
result$beta
result$y_pred
result$sigma2
result$variance_beta
result$confint
result$r_sqrd
result$mallow_cp
result$f_stat
result$pf_value
```
